Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
Placeholder for tables

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
        by \hscpipe{} PSF photometry.
        Hexagonal binned density plots and contours show the distributions for
        stars in both the good- and bad-seeing \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes.
        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
        respectively.
        The left panel in each plot shows the relation between input magnitude and
        magnitude difference.
        Hexagonal binned density plots and contours are for the synthetic galaxies 
        from good and bad seeing \tracts{}.
        Highly blended objects are highlighted using scattered points.
        The long-dashed lines mark zero magnitude difference, while the pairs of
        dashed lines outline the running-median of PSF magnitude errors
        (including the uncertainties in aperture correction).
        The right panel in each plot shows the distributions of the magnitude 
        differences for objects in good (filled) and bad (solid line) seeing \tracts{}.
        The dashed lines identify the distribution of highly blended objects.
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Besides seeing, the degree to which an object is blended with other objects 
    is another factor that influences photometric accuracy. 
    To quantify the impact of blending effects, we use the ``blendedness'' 
    parameter, $b$. 
    This parameter describes how much any given object overlaps with neighboring 
    objects (see Appendix \ref{app:defineb} and Murata\etal in prep.). 
    We divide our sample according to the blendedness parameter. 
    A value of $b=0$ corresponds to isolated objects whereas objects with $b=1$ 
    complete overlap with other objects. 
    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended
    according to this criterion).
    The fraction of highly blended stars slightly increases in the bad seeing \tract{}. 
    The impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.

@@

    Fig \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
    sources at fixed input magnitude.
    In $i$-band, the bad-seeing (0.7\asec{}) \tract{} shows systematically
    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
    seeing conditions.

@@

	The precisions and accuracies of \forced{} PSF magnitudes shown here are 
	summarized in Table \ref{tab:mag}

@@

	The statistical uncertainties of \forced{} PSF colors are summarized in 
	Table \ref{tab:color}

@@

    We find that \hscpipe{} mis-classifies lower than $1$\% of these objects as 
    point sources in the good-seeing \tract{}.
    But the fraction of misclassified galaxies increases to $4$\% in the
    bad-seeing \tract{}. 
    We will discuss star/galaxy separation further in Section \ref{ssec:sg}.

@@

	The precisions and accuracies of \forced{} \cmodel{} magnitudes shown here are 
	summarized in Table \ref{tab:mag}

@@

	The statistical uncertainties of \forced{} \cmodel{} colors are summarized in 
	Table \ref{tab:color}

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. 
        Star--galaxy separation is based on the the magnitude difference between the 
        PSF and \cmodel{} photometry. 
        The plot on the \textbf{left} (a) corresponds to synthetic stars. 
        Hexagonal bins and filled histogram show distributions of correctly classified
        synthetic stars in the good-seeing \tract{}.
        The scatter plot (dashed-line histogram) and contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
        Hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
        respectively.
        The scatter plot and dashed-line histogram highlight synthetic galaxies that 
        are misclassified as point sources.}
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

@@

%% ------------------------------------------------------------------------------------ %%
%%%%%%%%%%%: Possible Tables %%%%%%%%%%%%%
%\input{table1.tex}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
        by \hscpipe{} PSF photometry.
        Hexagonal binned density plots and contours show the distributions for
        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes.
        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
        respectively.
        The left panel in each plot shows the relation between input magnitude and
        magnitude difference.
        Hexagonal binned density plots and contours are for the synthetic galaxies 
        from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
        Highly blended objects are highlighted using scattered points.
        The long-dashed lines mark zero magnitude difference, while the pairs of
        dashed lines outline the running-median of PSF magnitude errors
        (including the uncertainties in aperture correction).
        The right panel in each plot shows the distributions of the magnitude 
        differences for objects in \texttt{goodSeeing} (filled) and \texttt{badSeeing}
        (solid line) \tracts{}.
        The dashed lines identify the distribution of highly blended objects.
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Besides seeing, the degree to which an object is blended with other objects 
    is another factor that influences photometric accuracy. 
    To quantify the impact of blending effects, we use the ``blendedness'' 
    parameter, $b$. 
    This parameter describes how much any given object overlaps with neighboring 
    objects (see Appendix \ref{app:defineb} and Murata\etal in prep.). 
    We divide our sample according to the blendedness parameter. 
    A value of $b=0$ corresponds to isolated objects whereas objects with $b=1$ 
    complete overlap with other objects. 
    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended
    according to this criterion).
    The fraction of highly blended stars slightly increases in the \texttt{badSeeing} 
    \tract{}. 
    The impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.

@@

    Fig \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
    sources at fixed input magnitude.
    In $i$-band, the \texttt{badSeeing} (0.70\asec{}) \tract{} shows systematically
    lower \s2n{} than the \texttt{goodSeeing} (0.45\asec{}) \tract{}.
    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
    seeing conditions.

@@

	The precisions and accuracies of \forced{} PSF magnitudes shown here are 
	summarized in Table \ref{tab:psfmag}

@@

	The statistical uncertainties of \forced{} PSF colors are summarized in 
	Table \ref{tab:psfcolor}

@@

    We find that \hscpipe{} mis-classifies lower than $1$\% of these objects as 
    point sources in the \texttt{goodSeeing} \tract{}.
    But the fraction of misclassified galaxies increases to $4$\% in the
    \texttt{goodSeeing} \tract{}. 
    We will discuss star/galaxy separation further in Section \ref{ssec:sg}.

@@

	The precisions and accuracies of \forced{} \cmodel{} magnitudes shown here are 
	summarized in Table \ref{tab:cmodelmag}

@@

	The statistical uncertainties of \forced{} \cmodel{} colors are summarized in 
	Table \ref{tab:cmodelcolor}

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. 
        Star--galaxy separation is based on the the magnitude difference between the 
        PSF and \cmodel{} photometry. 
        The plot on the \textbf{left} (a) corresponds to synthetic stars. 
        Hexagonal bins and filled histogram show distributions of correctly classified
        synthetic stars in the \texttt{goodSeeing} \tract{}.
        The scatter plot (dashed-line histogram) and contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
        Hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
        respectively.
        The scatter plot and dashed-line histogram highlight synthetic galaxies that 
        are misclassified as point sources.}
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} PSF colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:psfcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} \cmodel{} magnitudes in 
        all five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} \cmodel{} colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:cmodelcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

@@
